Evaluating FAIR Digital Object as a distributed object system

### 2023-02-01 latex/main.tex
tiny URL fonts
please give me xelatex..
reordered FDO section

@@

FDO is an evolving concept. A set of FDO Demonstrators \cite{jRWurmQc} highlight how current adapters are approaching implementations of FDO from different angles:

\begin{itemize}
\tightlist
\item
  Building on the Digital Object concept, using the simplified DOIP v2 specification \cite{13TcbsZF6}, which detail how to exchange JSON objects through a text-based protocol\footnote{For a brief introduction to DOIP 2.0, see \cite{xuQKRRx5}} (usually TCP/IP over TLS). The main DOIP operations are retrieving, creating and updating digital objects. These are mostly realised using the reference implementation \href{https://cordra.org/}{Cordra}. FDO types are registered in the local Cordra instance, where they are specified using JSON Schema \cite{15EZ2D0Rm} and PIDs are assigned using the Handle system. Several type registries have been established.
\item
  Following the traditional Linked Data approach, but using the DOIP protocol, e.g.~using JSON-LD and schema.org within DOIP (NIST for material science).
\item
  Approaching the FDO principles from existing Linked Data practices on the Web (e.g.~WorkflowHub use of RO-Crate and schema.org).
\end{itemize}

>>>>

FDO is an evolving concept. A set of FDO Demonstrators \autocite{wittenburgFAIRDigitalObject2022b} highlight how current adapters are approaching implementations of FDO from different angles:

\begin{itemize}
\tightlist
\item
  Building on the Digital Object concept, using the simplified DOIP v2 specification \autocite{foundationDigitalObjectInterface}, which detail how to exchange JSON objects through a text-based protocol\footnote{For a brief introduction to DOIP 2.0, see \autocite{DOIPExamplesCordraa}} (usually TCP/IP over TLS). The main DOIP operations are retrieving, creating and updating digital objects. These are mostly realised using the reference implementation \href{https://cordra.org/}{Cordra}. FDO types are registered in the local Cordra instance, where they are specified using JSON Schema \autocite{Draftbhuttonjsonschema00} and PIDs are assigned using the Handle system. Several type registries have been established.
\item
  Following the traditional Linked Data approach, but using the DOIP protocol, e.g.~using JSON-LD and schema.org within DOIP (NIST for material science).
\item
  Approaching the FDO principles from existing Linked Data practices on the Web (e.g.~WorkflowHub use of RO-Crate and schema.org).
\end{itemize}

@@
